On Secure Delegation of SampBQP with a Classical Client

### 2020-03-30 hamiltonian.tex
Clarify wording

	Define $c$ so that $\cVGS$ accepts $\ket{\phi}$ with probability $\frac{1}{2}-\frac{c}{T^5}\braket{\phi|H_{C(x)}|\phi}$.
	Break $\ket{\phi}$ above into what's in the kernel of $H$ and what isn't:
	$$\ket{\phi}=\braket{\psi_{C(x)}|\phi}\ket{\phi_K}+\sqrt{1-\abs{\braket{\psi_{C(x)}|\phi}}^2}\ket{\phi_{K^\bot}}$$
	We can then see $\braket{\phi|H|\phi}=1-\abs{\braket{\psi_{C(x)}|\phi}}^2=1-F(\ket{\psi_{C(x)}}, \ket{\phi})$.
	This argument above can be generalized for mixed states since we have for all $\sigma$ that
	$$F(\sum_i p_i \ket{\phi_i}\bra{\phi_i}, \sigma)=\sum_i p_i F(\ket{\phi_i}, \sigma)$$
	Now we have
	$$p_{acc}=\frac{1}{2}-\frac{c}{T^5}(1-F(\ket{\psi_{C(x)}}, \rho))\geq\frac{1}{2}-\frac{c\varepsilon}{T^5}$$
	which implies our claim.
\end{prf}

>>>>

	Define $c$ so that $\cVGS$ accepts $\ket{\phi}$ with probability $\frac{1}{2}-\frac{c}{T^5}\braket{\phi|H_{C(x)}|\phi}$.
	Break $\ket{\phi}$ above into what's in the kernel of $H$ and what isn't:
	$$\ket{\phi}=\braket{\psi_{C(x)}|\phi}\ket{\phi_K}+\sqrt{1-\abs{\braket{\psi_{C(x)}|\phi}}^2}\ket{\phi_{K^\bot}}$$
	We can then see
	$$\braket{\phi|H|\phi}=1-\abs{\braket{\psi_{C(x)}|\phi}}^2=1-F(\ket{\psi_{C(x)}}, \ket{\phi})$$
	which can be generalized for mixed states since we have for all $\ket\psi$ that
	$$F(\sum_i p_i \ket{\phi_i}\bra{\phi_i}, \ket\psi)=\sum_i p_i F(\ket{\phi_i}, \ket\psi).$$
	As a result, we have
	$$p_{acc}=\frac{1}{2}-\frac{c}{T^5}(1-F(\ket{\psi_{C(x)}}, \rho))\geq\frac{1}{2}-\frac{c\varepsilon}{T^5}$$
	which implies our claim.
\end{prf}
